---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "80%"
)
```

# adjusted

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/adjusted)](https://CRAN.R-project.org/package=adjusted)
[![R-CMD-check](https://github.com/topepo/adjusted/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/topepo/adjusted/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/topepo/adjusted/branch/main/graph/badge.svg)](https://app.codecov.io/gh/topepo/adjusted?branch=main)
<!-- badges: end -->

The goal of adjusting is to make better predictions for regression models by adjusting them using the most similar points from the training set. We implement the method of [Quinlan (1993)](https://scholar.google.com/scholar?hl=en&as_sdt=0%2C7&q=combining+instance%E2%80%93based+and+model%E2%80%93based+learning&btnG=) and the [Gower distance](https://scholar.google.com/scholar?hl=en&as_sdt=0%2C7&q=A+general+coefficient+of+similarity+and+some+of+its+properties&btnG=). 

## Installation

You can install the development version of adjusted like so:

``` r
pak::pak("topepo/adjusted)
```

## Example

Let’s model the motorcycle helmet data in the `MASS` package with a regression tree as an example. First, the data and the original CART fit: 

```{r}
library(adjusted)
library(workflows)
library(dplyr)
library(parsnip)
library(ggplot2)

# Use the 1D motorcycle helmet data as an example

data(mcycle, package = "MASS")

# Use every fifth data point as a test point
in_test <- ( 1:nrow(mcycle) ) %% 5 == 0
cycl_train <- mcycle[-in_test, ]
cycl_test  <- mcycle[ in_test, ]

# A grid to show the predicted lines
mcycle_grid <- tibble(times = seq(2.4, 58, length.out = 500))
```

There is a nonlinear relationship between the predictor and outcome:

```{r training}
theme_set(theme_bw())

cycl_train %>%
  ggplot(aes(x = times)) +
  geom_point(aes(y = accel))
```

The CART fit is, as expected, blocky:

```{r raw}
cart_spec <- decision_tree() %>% set_mode("regression")

cart_fit <- 
  workflow(accel ~ times, cart_spec) %>% 
  fit(data = cycl_train)

raw_pred <- augment(cart_fit, mcycle_grid)

raw_pred %>% 
  ggplot(aes(x = times)) + 
  geom_point(data = cycl_test, aes(y = accel)) +
  geom_line(aes(y = .pred),  col = "blue", alpha = 3 / 4)
```

The `nn_adjust()` function collects the information that it needs by storing the fitted workflow as well as the training set: 

```{r}
adj_obj <- nn_adjust(cart_fit, cycl_train)
```

The `predict()` or `augment()` methods can be used to make the original prediction along with the adjustment. The number of neighbors is specified here: 

```{r}
adj_obj <- nn_adjust(cart_fit, cycl_train)
adj_pred <- augment(adj_obj, mcycle_grid, neighbors = 10)
head(adj_pred)
```

For the held out data, there are different predictions: 

```{r adjusted}
adj_pred %>% 
  ggplot(aes(x = times)) + 
  geom_point(data = cycl_test, aes(y = accel)) +
  geom_line(aes(y = .pred),  col = "darkorange", alpha = 3 / 4)
```

## Code of Conduct
  
Please note that the adjusted project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
  
